An Exegesis of Ontological Hermeneutics

### 2023-02-09 paper.tex
1/4gamma avg BPSK found

\documentclass[12pt]{report} % add 'draft' to suppress figures
% Double-spaced, single-column format for IEEE journal submission
% \documentclass[12pt,journal,draftclsnofoot,onecolumn]{IEEEtran} 
\usepackage{wrapfig,booktabs,fancyhdr,amsmath,amsfonts,tabularx,numprint}
\usepackage{cite,bm,bbm,amssymb,amsthm,url,multirow,times,enumitem,comment}
\usepackage{mathtools,siunitx,balance,tikz,adjustbox,graphicx,array}
\usepackage[font=footnotesize]{subcaption}
\usepackage[linesnumbered,ruled]{algorithm2e}
\usepackage[colorlinks=true, linkcolor=black, citecolor=blue, urlcolor=blue]{hyperref}
\usepackage{geometry}
 \geometry{
 a4paper,
 total={170mm,257mm},
 left=20mm,
 top=20mm,
 }
 \usepackage[acronym,nomain,nonumberlist]{glossaries}
 \makeglossaries

@@

\newacronym{PL}{PL}{Path loss}
\newacronym{LOS}{LOS}{Line of sight}
\newacronym{NLOS}{NLOS}{Non-line of sight}
\newacronym{BW}{BW}{Bandwidth}
\newacronym{iid}{i.i.d.}{independent and identically-distributed}
\newacronym{CLT}{CLT}{Central Limit Theorem}
\newacronym{GRV}{GRV}{Gaussian random variable}
\newacronym{SNR}{SNR}{signal-to-noise ratio}
\newacronym{PSD}{PSD}{power spectral density}
\glsaddall

@@

where $\beta$ acts as the mean distance before blocking occurs (i.e. by a building), and the $PL_{LOS}$ and $PL_{NLOS}$ terns are functions for \gls{PL} models.

@@

\begin{align}
  SNR = \frac{P_r}{P_t} = \left\{ \begin{array}{ll}
                                    K_0 \left[\frac{1}{100}\right]^2     & \text{w.p.} ~~~~~~ e^{-100/25}  \\
                                    K_0 \left[\frac{1}{100}\right]^{2.5} & \text{w.p.} ~~~ 1 - e^{-100/25} \\
                                  \end{array}
  \right. \nonumber
  = \left\{ \begin{array}{ll}
              -80 \text{ dB} & \text{w.p.} ~ 0.0183 \\
              -90 \text{ dB} & \text{w.p.} ~ 0.9817 \\
            \end{array}
  \right. \nonumber
\end{align}

@@

\subsection*{Shadowing example}
Imagine a scenario in which we wish to evaluate Wi-Fi coverage for a desired
range of $100$ m, with a minimum $SNR = 5$ dB and outage constraint at $1\%$ for
the $5$ GHz frequencies. The \gls{PL} is modeled as exponential with $\alpha =
  3$, $K = K_0 = -50$ dB (for $F_c \approx 5$ GHz), no TX and RX gain, a noise
power of $P_n = -100$ dBm and a shadowing standard deviation of
$\sigma_{\text{dB}} = 6$. What is the mimum transmition power to meet the outage
constraint?
\\
\\
Answer:

@@

\begin{align}
  P(P_{t,\text{dB}} \geq  15 - x_{\text{dB}}) = 1 - 0.01 \nonumber \\
  15 - P_{t,\text{dB}} = \sigma_{\text{dB}}Q^{-1}(0.99) \nonumber  \\
  P_{t,\text{dB}} \geq 29 \text{ dBm} \nonumber
\end{align}

\chapter{Multipath Channel Models}
\label{multipath_ch_model}
A transmitted signal $s(t)$ propagates through an environment in multiple paths.
Neglecting noise, the received signal is simply a sum of attenuated, delayed,
and phase shifted versions of the original transmitted signal. The different
paths a signal takes to get to a receiver results in a sum with patterns of high
or low destructive interference, an effect called multipath fading.
\section{Multipath Model}
We model the channel $c(\tau,t)$ as a time-varying ($t$) impulse response function evaluated at $t - \tau$. As with any system, the received signal is modeled as a convolution of $c(\tau,t)$ with the transmitted signal $s(t)$.

@@

\section{Probability of Error}
TODO

The probability of error $P_s$ is defined in a per-symbol basis. Each constellation has a different $P_s$, seen in the table below based on the Nearest Neighbor bound.

\begin{table}[htbp]
  \centering
  \caption{}
  \begin{tabular}{lcccc}                                                                                \\
    \cmidrule(r){1-3} & $P_s(\gamma_s)$                                  & $P_b(\gamma_b)$ \\
    \midrule MPAM     & $2(1-1/M)Q(\sqrt{\frac{3\gamma_s}{M^2-1}})$      &                 \\
    \midrule MPSQ     & $2Q(\sqrt{2\gamma_s}\sin(\pi/M))$                                  \\
    \midrule MQAM     & $4(1-1/\sqrt{M})Q(\sqrt{\frac{3\gamma_s}{M-1}})$                   \\
    \midrule FSK      & $(M-1)Q(\sqrt(\gamma_s/2))$                                        \\
    \\

    \bottomrule
  \end{tabular}
  \label{tab:constellation_pe}
\end{table}

@@

@@

% \bibliographystyle{ieeetran}
% \bibliography{ref}
\end{document}

>>>>

\documentclass[12pt]{report} % add 'draft' to suppress figures
% Double-spaced, single-column format for IEEE journal submission
% \documentclass[12pt,journal,draftclsnofoot,onecolumn]{IEEEtran} 
\usepackage{wrapfig,booktabs,fancyhdr,amsmath,amsfonts,tabularx,numprint}
\usepackage{cite,bm,bbm,amssymb,amsthm,url,multirow,times,enumitem,comment}
\usepackage{mathtools,siunitx,balance,tikz,adjustbox,graphicx,array}
\usepackage[font=footnotesize]{subcaption}
\usepackage[linesnumbered,ruled]{algorithm2e}
\usepackage[colorlinks=true, linkcolor=black, citecolor=blue, urlcolor=blue]{hyperref}
\usepackage{geometry}
 \geometry{
 a4paper,
 total={170mm,257mm},
 left=20mm,
 top=20mm,
 }
 \usepackage[acronym,nomain,nonumberlist]{glossaries}
 \makeglossaries
 \usepackage{mdframed}

@@

\newacronym{PL}{PL}{Path loss}
\newacronym{LOS}{LOS}{Line of sight}
\newacronym{NLOS}{NLOS}{Non-line of sight}
\newacronym{BW}{BW}{Bandwidth}
\newacronym{iid}{i.i.d.}{independent and identically-distributed}
\newacronym{CLT}{CLT}{Central Limit Theorem}
\newacronym{GRV}{GRV}{Gaussian random variable}
\newacronym{SNR}{SNR}{signal-to-noise ratio}
\newacronym{PSD}{PSD}{power spectral density}
\newacronym{BER}{BER}{bit error rate}
\newacronym{AWGN}{AWGN}{additive white Gaussian noise}

\glsaddall

@@

where $\beta$ acts as the mean distance before blocking occurs (i.e. by a building), and the $PL_{LOS}$ and $PL_{NLOS}$ terns are functions for \gls{PL} models.
\begin{mdframed}

@@

  \begin{align}
    SNR = \frac{P_r}{P_t} = \left\{ \begin{array}{ll}
                                      K_0 \left[\frac{1}{100}\right]^2     & \text{w.p.} ~~~~~~ e^{-100/25}  \\
                                      K_0 \left[\frac{1}{100}\right]^{2.5} & \text{w.p.} ~~~ 1 - e^{-100/25} \\
                                    \end{array}
    \right. \nonumber
    = \left\{ \begin{array}{ll}
                -80 \text{ dB} & \text{w.p.} ~ 0.0183 \\
                -90 \text{ dB} & \text{w.p.} ~ 0.9817 \\
              \end{array}
    \right. \nonumber
  \end{align}
\end{mdframed}

@@

\begin{mdframed}
  \subsection*{Shadowing example}
  Imagine a scenario in which we wish to evaluate Wi-Fi coverage for a desired
  range of $100$ m, with a minimum $SNR = 5$ dB and outage constraint at $1\%$ for
  the $5$ GHz frequencies. The \gls{PL} is modeled as exponential with $\alpha =
    3$, $K = K_0 = -50$ dB (for $F_c \approx 5$ GHz), no TX and RX gain, a noise
  power of $P_n = -100$ dBm and a shadowing standard deviation of
  $\sigma_{\text{dB}} = 6$. What is the mimum transmition power to meet the outage
  constraint?
  \\
  \\
  Answer:

@@

  \begin{align}
    P(P_{t,\text{dB}} \geq  15 - x_{\text{dB}}) = 1 - 0.01 \nonumber \\
    15 - P_{t,\text{dB}} = \sigma_{\text{dB}}Q^{-1}(0.99) \nonumber  \\
    P_{t,\text{dB}} \geq 29 \text{ dBm} \nonumber
  \end{align}
\end{mdframed}
\chapter{Multipath Channel Models}
\label{multipath_ch_model}
A transmitted signal $s(t)$ propagates through an environment in multiple paths.
Neglecting noise, the received signal is simply a sum of attenuated, delayed,
and phase shifted versions of the original transmitted signal. The different
paths a signal takes to get to a receiver results in a sum with patterns of high
or low destructive interference, an effect called multipath fading.
\section{Multipath Model}
We model the channel $c(\tau,t)$ as a time-varying ($t$) impulse response function evaluated at $t - \tau$. As with any system, the received signal is modeled as a convolution of $c(\tau,t)$ with the transmitted signal $s(t)$.

@@

\section{Probability of Error for fixed SNR}
TODO

The probability of error $P_s$ is defined in a per-symbol basis. Each constellation has a different $P_s$, seen in the table below based on the Nearest Neighbor bound in an \gls{AWGN} channel.

\begin{table}[htbp]
  \centering
  \caption{}
  \begin{tabular}{lcccc}                                                                                                                                            \\
    \cmidrule(r){1-3} & $P_s(\gamma_s)$                                  & $P_b(\gamma_b)$                                                             \\
    \midrule MPAM     & $2(1-1/M)Q(\sqrt{\frac{6\gamma_s}{M^2-1}})$      & $\frac{2(1-1/M)}{\log_{2}M}Q(\sqrt{\frac{6\gamma_b\log_{2}M}{M^2-1}})$      \\
    \midrule MPSQ     & $2Q(\sqrt{2\gamma_s}\sin(\pi/M))$                & $\frac{2}{\log_{2}M}Q(\sqrt{2\gamma_b\log_{2}M}\sin(\pi/M))$                \\
    \midrule MQAM     & $4(1-1/\sqrt{M})Q(\sqrt{\frac{3\gamma_s}{M-1}})$ & $\frac{4(1-1/\sqrt{M})}{\log_{2}M}Q(\sqrt{\frac{3\gamma_b\log_{2}M}{M-1}})$ \\
    \midrule FSK      & $(M-1)Q(\sqrt{\gamma_s/2})$                      & $\frac{(M-1)}{\log_{2} M}Q(\sqrt{\gamma_b \log_{2} M/2})$                   \\
    \bottomrule
  \end{tabular}
  \label{tab:constellation_pe}
\end{table}

Where generally $P_b = P_s / \log{2}(M)$ for Gray coded constellations.

@@

Another way to more easily calculate

\section{Probability of Error for stochastic SNR}
Since the SNR depends on the received power, which in turn depends on the
affects of blocking, shadowing, and fading, the SNR is a random variable. It
becomes useful then to define the average \gls{BER}.

\begin{align}
  \overline{P_b}  \triangleq \E{P_b} = \int_0^{\infty} P_{b}(\gamma) f_{\gamma}(\gamma) d\gamma
\end{align}
\begin{mdframed}

  \subsection*{Average BPSK in Rayleigh Fading}
  Express the average \gls{BER} of a BPSK signal in a Rayleigh fading channel in terms of the averge SNR $\overline{\gamma}$.
  \\
  \\
  Answer: \\
  For Rayleigh fading:
  \begin{align}
    f_{\gamma_s}(\gamma) = \frac{1}{\overline{\gamma}} e^{-\gamma/\overline{\gamma}}\nonumber
  \end{align}
  And for BPSK:
  \begin{align}
    P_b(\gamma_s) = 2Q(\sqrt{2\gamma_s}) \nonumber
  \end{align}

  So the \gls{BER} is:
  \begin{align}
    \overline{P_b} & = \int_0^{\infty} 2Q(\sqrt{2\gamma}) \frac{1}{\overline{\gamma}} e^{-\gamma/\overline{\gamma}} d\gamma \nonumber
  \end{align}
  with change of variables $x = \gamma/\overline{\gamma}$ such that $d \gamma/\overline{\gamma} = d x $

  \begin{align}
    \overline{P_b} & = \int_0^{\infty} 2Q(\sqrt{2x\overline{\gamma}}) e^{-x} dx \nonumber                                         \\
                   & = \frac{2}{2\pi} \int_0^{\infty} e^{-x} \int_{\sqrt{2x\overline{\gamma}}}^{\infty} e^{-t^2/2} dtdx \nonumber
  \end{align}
  and switching the order of the integrals
  \begin{align}
    \overline{P_b} & = \frac{1}{\pi} \int_0^{\infty} \int_{0}^{t^2/(2\overline{\gamma})} e^{-t^2/2} e^{-x}  dxdt \nonumber \\
                   & = \frac{1}{\pi} \int_0^{\infty} e^{-t^2/2}(1-e^{t^2/(2\overline{\gamma})}) dt \nonumber               \\
                   & = \frac{1}{2} - \frac{1}{1\pi} \int_0^{\infty} e^{-t^2(1+1/\overline{\gamma})/2} dt \nonumber         \\
                   & = \frac{1}{2} \left( 1-\sqrt{\frac{\overline{\gamma}}{1+\overline{\gamma}}}\right) \nonumber          \\
                   & \approxeq \frac{1}{4\overline{\gamma}} \nonumber
  \end{align}
\end{mdframed}

As seen in the example above it can become cumbersome to calculate the average bit error rate. To expedite the process we can use the moment generating functions of the channels and simplify the integral. Most constellation bit error probabilities can be approximated or precisely expressed as $$P_b(\gamma) = a Q( \sqrt{\beta\gamma})$$

Using \cite{Craig258319}, we can express the $Q$-function as
\begin{align}
  Q(x) = \frac{1}{\pi}\int_{0}^{\pi/2} e^{-\frac{x^2}{2 \sin^2\phi}}d\phi
\end{align}

@@

\bibliographystyle{ieeetran}
\bibliography{ref}
\end{document}
